CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2023-12-20 paper.Rmd
AggDatabase --> AggPipeline

The steps to create the PSUT matrices for each country and each year
are accomplished by a
[targets][link-targets] [@Landau:2021aa]
computation pipeline
available in the [PFUPipeline][link-pfupipeline]
package.
A unique feature of the
[PFUPipeline][link-pfupipeline]
pipeline enabled by the [Recca][link-recca] package 
is an innovative exemplar system that allows
analyses to proceed when allocation or efficiency data are unavailable for a country.
When allocations or efficiencies are missing,
a string of exemplar countries or regions
are queried for the required information.
For example, exemplars for Belgium are
France, Europe, and ultimately, the World, in that order.
The design of the calculation pipeline in the [PFUPipeline][link-pfupipeline] package 
allows allocation and efficiency data
for any country or year to be added at a later date 
to improve the database.

A second [targets][link-targets] pipeline 
in the [PFUAggPipeline][link-pfuaggpipeline] package [@Heun-PFUAggPipeline:2023]
aggregates ECCs
(a) by region 
(e.g., continents and world),
(b) by energy carrier (product) category 
(e.g., Coal and coal products, 
Low-, Medium-, and High-temperature heat, etc.), 
(c) by energy conversion machines (industries) and/or end use sectors
(e.g., Residential, Transport, etc.), and
(d) to primary, final, and useful (PFU) stages.
In addition, the [PFUAggDatabase][link-pfuaggdatabase] pipeline 
calculates efficiencies for each country
at all available aggregations.
The [PFUAggDatabase][link-pfuaggdatabase]
pipeline uses the [Recca][link-recca] package extensively.

>>>>

The steps to create the PSUT matrices for each country and each year
are accomplished by a
[targets][link-targets] [@Landau:2021aa]
computation pipeline
available in the [PFUPipeline][link-pfupipeline]
package.
A unique feature of the
[PFUPipeline][link-pfupipeline]
enabled by the [Recca][link-recca] package 
is an innovative exemplar system that allows
analyses to proceed when allocation or efficiency data are unavailable for a country.
When allocations or efficiencies are missing,
a string of exemplar countries or regions
are queried for the required information.
For example, exemplars for Belgium are
France, Europe, and ultimately, the World, in that order.
The design of the calculation pipeline in the [PFUPipeline][link-pfupipeline] package 
allows allocation and efficiency data
for any country or year to be added at a later date 
to improve the database.

A second [targets][link-targets] pipeline 
in the [PFUAggPipeline][link-pfuaggpipeline] package [@Heun-PFUAggPipeline:2023]
aggregates ECCs
(a) by region 
(e.g., continents and world),
(b) by energy carrier (product) category 
(e.g., Coal and coal products, 
Low-, Medium-, and High-temperature heat, etc.), 
(c) by energy conversion machines (industries) and/or end use sectors
(e.g., Residential, Transport, etc.), and
(d) to primary, final, and useful (PFU) stages.
In addition, the [PFUAggPipeline][link-pfuaggpipeline] 
calculates efficiencies for each country
at all available aggregations.
The [PFUAggPipeline][link-pfuaggpipeline]
uses the [Recca][link-recca] package extensively.
